### 2021-12-07 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@c674d297723af7b596895362aa1bc58859555e33 🚀

\begin{enumerate}
    \itemThe prediction of species interaction networks is gaining
momentum as a way to circumvent limitations in data volume. Yet,
ecological networks are challenging to predict because they are
typically small and sparse. Dealing with extreme class imbalance is a
challenge for most binary classifiers, and there are currently no
guidelines as to how predictive models can be trained.%
    \itemUsing simple mathematical arguments and numerical experiments
in which a variety of classifiers (for supervised learning) are trained
on simulated networks, we develop a series of guidelines related to the
choice of measures to use for model selection, and the degree of
unbiasing to apply to the training dataset.%
    \itemClassifier accuracy and the ROC-AUC are not informative
measures for the performance of interaction prediction. PR-AUC is a
fairer assesment of performance. In some cases, even standard measures
can lead to selecting a more biased classifier because the effect of
connectance is strong. The amount of correction to apply to the training
dataset depends as a function of the classifier and the network
connectance.%
    \itemThese results reveal that training machines to predict networks
is a challenging task, and that in virtually all cases, the composition
of the training set needs to be experimented on before performing the
actual training. We discuss these consequences in the context of the low
volume of data.%
\end{enumerate}

>>>>

\begin{enumerate}
    \item The prediction of species interaction networks is gaining
momentum as a way to circumvent limitations in data volume. Yet,
ecological networks are challenging to predict because they are
typically small and sparse. Dealing with extreme class imbalance is a
challenge for most binary classifiers, and there are currently no
guidelines as to how predictive models can be trained.%
    \item Using simple mathematical arguments and numerical experiments
in which a variety of classifiers (for supervised learning) are trained
on simulated networks, we develop a series of guidelines related to the
choice of measures to use for model selection, and the degree of
unbiasing to apply to the training dataset.%
    \item Classifier accuracy and the ROC-AUC are not informative
measures for the performance of interaction prediction. PR-AUC is a
fairer assesment of performance. In some cases, even standard measures
can lead to selecting a more biased classifier because the effect of
connectance is strong. The amount of correction to apply to the training
dataset depends as a function of the classifier and the network
connectance.%
    \item These results reveal that training machines to predict
networks is a challenging task, and that in virtually all cases, the
composition of the training set needs to be experimented on before
performing the actual training. We discuss these consequences in the
context of the low volume of data.%
\end{enumerate}
